H0LiCOW: correlation between black hole mass and host galaxy luminosity.

### 2020-02-25 manuscript/manuscript.tex
Update table print_table

@@

>>>>

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of lensed AGN information.}\label{data_set}
\resizebox{9cm}{!}{
     \begin{tabular}{cccccc}
        \hline
Object ID & z & camera & Filter & exposure & pixel scale \\
 & & & & time (s) & (drizzled) \\ \hline
HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & $0\farcs{}08$ \\
RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & $0\farcs{}05$ \\
WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & $0\farcs{}08$ \\
SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & $0\farcs{}08$ \\
HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & $0\farcs{}08$ \\
SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & $0\farcs{}03$ \\
HS2209$+$1914 & 1.07 & WFC3-UVIS & F814W & 14238 & $0\farcs{}03$ \\
HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & $0\farcs{}03$ \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ If any
\end{tablenotes}  
%\end{threeparttable}
\end{table}

@@

\begin{table*}
\renewcommand{\arraystretch}{1.5}
%\setlength{\tabcolsep}{20pt}
\centering
  \begin{threeparttable}
\caption{Summary of lensed AGN inference.}\label{data_set}    
%\resizebox{12cm}{!}{
     \begin{tabular}{ccccccc}
\hline
Object ID & Magnitude & Host-Total Flux Ratio & Reff & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
 & (AB system) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
HE0435 & $21.332\substack{+0.208\\-0.175}$ & $62.471\pm10.893$ & $0.298\pm0.027$ & $2.829\pm0.251$ & $1.500$ & $10.98\substack{+0.07\\-0.08}$ \\
RXJ1131$_{\rm bulge}$ & $22.074\substack{+0.164\\-0.142}$ & $6.634\pm0.929$ & $0.106\pm0.007$ & fix to 4 & $3.000$ & $1.01\substack{+0.06\\-0.07}$ \\
RXJ1131$_{\rm disk}$ & $19.305\substack{+0.154\\-0.135}$ & $84.939\pm11.241$ & $0.875\pm0.062$ & fix to 1 & $1.500$ & $1.04\substack{+0.05\\-0.06}$ \\
WFI2033 & $21.404\substack{+0.167\\-0.145}$ & $35.723\pm5.093$ & $0.294\pm0.025$ & $0.528\pm0.011$ & $0.625$ & $10.66\substack{+0.06\\-0.07}$ \\
SDSS1206 & $21.287\substack{+0.222\\-0.184}$ & $32.286\pm5.977$ & $0.110\pm0.020$ & $4.526\pm0.555$ & $0.625$ & $10.78\substack{+0.07\\-0.09}$ \\
HE1104 & $21.274\substack{+0.188\\-0.160}$ & $14.142\pm2.250$ & $0.265\pm0.026$ & $1.033\pm0.034$ & $0.625$ & $11.04\substack{+0.06\\-0.08}$ \\
SDSS0246 & $23.575\substack{+0.394\\-0.289}$ & $3.756\pm1.143$ & $0.381\pm0.098$ & $4.963\pm0.048$ & $0.626$ & $10.69\substack{+0.12\\-0.16}$ \\
HS2209 & $20.385\substack{+0.262\\-0.211}$ & $19.454\pm4.165$ & $1.921\pm1.070$ & $2.953\pm0.438$ & $1.001$ & $11.18\substack{+0.08\\-0.10}$ \\
HE0047 & $22.972\substack{+0.626\\-0.394}$ & $2.496\pm1.093$ & $0.282\pm0.176$ & $3.603\pm1.533$ & $0.625$ & $10.89\substack{+0.16\\-0.25}$ \\
\hline
\end{tabular}
%}
\begin{tablenotes}
      \small
      \item Note: $-$ If any
\end{tablenotes}    
\end{threeparttable}
\end{table*}
